Meta-analysis

### 2020-06-23 04_MetaAnalysis.Rmd
Add meta-evaluation of disease pressure

```{r metafor_organisation}
dat1 <-
   slimmer_PM_dat %>%
   filter(fungicide_ai != "control") %>% #remove controls from the data
   mutate(spray_management =
             factor(
                spray_management,
                c(
                   "Early",
                   "Recommended",
                   "Recommended_plus",
                   "Late",
                   "Late_plus"
                )
             )) %>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype ,
      spray_management,
      fungicide_ai,
      D_pres,
      grain_yield.t.ha,
      grain_SMD,
      vi,
      vi2
      )
```

@@

```{r metafor_plot}
efficacy %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = seq(-0.5, 1.5, by = 0.2),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()
```

@@

>>>>

```{r metafor_organisation}
dat1 <-
   slimmer_PM_dat %>%
   filter(fungicide_ai != "control") %>% #remove controls from the data
   mutate(spray_management =
             factor(
                spray_management,
                c(
                   "Early",
                   "Recommended",
                   "Recommended_plus",
                   "Late",
                   "Late_plus"
                )
             ),
          D_pres = 
             factor(D_pres,
                    c("lowD",
                      "highD"))) %>%
   select(
      trial,
      trial_ref,
      location,
      year,
      row_spacing,
      host_genotype ,
      spray_management,
      fungicide_ai,
      D_pres,
      grain_yield.t.ha,
      grain_SMD,
      vi,
      vi2
      )
```

@@

```{r metafor_plot}
efficacy %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = seq(-0.5, 1.5, by = 0.2),
      color = usq_cols("usq charcoal"),
      linetype = 3
   ) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()

max(slimmer_PM_dat[slimmer_PM_dat$cluster_1 == "Late" &
                      ,"fungicide_timing_1"], na.rm = TRUE)
```

@@

### Disease pressure effect

We also want to know if disease pressure exerts an effect on the desicion for spray control.
Above we can see spraying at the first sign of powdery mildew or with in `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"| slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` - `r min(as.numeric(slimmer_PM_dat[slimmer_PM_dat$spray_management == "Late"|                   slimmer_PM_dat$spray_management == "Late_plus","fungicide_timing_1"]))` days after first sign is effective at mitigating yield loss.
Does this change between years of low and high disease pressure.

We will add the intercept back into this model for ease of interpretation. 
```{r D_pres-Meta}
PM_mv_Dp <- rma.mv(
   yi = grain_SMD,
   vi,
   mods = ~ spray_management *D_pres,
   method = "ML",
   random = ~ spray_management | trial,
   struct = "UN",
   data = dat1
)

summary(PM_mv_Dp)
```

These results show that the spray management variable we tested are not significantly better or worse between the two levels of disease pressure.
It also shows that in trials with high disease pressure all treatments produced lower standardised mean differences. 
Indicating that fungicide treatments were less effective at mitigating yeild loss in seasons which developed heavier infestations.  
Finally lets compare the disease pressure model to the orignal model to see which one fits better.

```{r compareDvNDP}
anova(PM_mv, PM_mv_Dp)
```
No significant difference which informs us to use the origninal model `PM_mv` which is the simplest.

****
